Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
Changed 2.20 and 2.25.

\begin{lemma}
\label{lem:bijectionMeshMutations}
There is precisely one non-initial mesh directed by each positive $\b{c}$-vector of the cluster algebra~$\principalClusterAlgebra[\B_\circ^\vee]$. Therefore~$|\principalVariables| = |\meshes| + n$.
\end{lemma}

@@

We also obtain from \cref{thm:extremalExchangeablePairsCA} the following surprising property.

\begin{corollary}
Any positive dual $\b{c}$-vector supports exactly one extremal exchangeable pair.
\end{corollary}

>>>>

\begin{lemma}
\label{lem:bijectionMeshMutations}
We have that~$|\principalVariables| = |\meshes| + n$.
\end{lemma}
\begin{proof}
 We postpone the proof until \pg{ref to later}.
\end{proof}

@@

As a follow-up to \cref{thm:extremalExchangeablePairsCA}, we conjecture the following surprising property.

\begin{conjecture}
Any positive dual $\b{c}$-vector supports exactly one extremal exchangeable pair.
\end{conjecture}
